THESIS PROJECT PROPOSAL

### 2019-11-08 project_ashish/paper.tex
commit

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd11.png}
  \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
   \label{figure 1}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Higgs production using the top quark (left) and W boson (right).}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
   \label{figure 8}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
  \caption{Standard model Higgs boson production cross section in various production modes.}
   \label{figure 11}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
   \label{figure 12}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
  \caption{Standard model Higgs boson branching ratios in various decay channels.}
   \label{figure 13}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
   \label{figure 14}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
   \label{figure 15}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
   \label{figure 16}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
   \label{figure 17}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
energy.}
   \label{figure 18}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
   \label{figure 19}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 20}
\end{figure}

>>>>

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd11.png}
  \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
   \label{figure 1}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
  \caption{Higgs production using the top quark (left) and W boson (right).}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
   \label{figure 8}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms7.jpg}
  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd.png}
  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd1.png}
  \caption{Standard model Higgs boson production cross section in various production modes.}
   \label{figure 11}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
   \label{figure 12}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd3.png}
  \caption{Standard model Higgs boson branching ratios in various decay channels.}
   \label{figure 13}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd5.png}
  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
   \label{figure 14}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd6.png}
  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
   \label{figure 15}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
   \label{figure 16}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th.png}
  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
   \label{figure 17}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th1.png}
  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
energy.}
   \label{figure 18}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th2.png}
  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
   \label{figure 19}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th3.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 20}
\end{figure}
